---
title: "Diabetes Diagnosis"
author: "Jaeyoon Han"
output:
  html_document:
    highlight: pygments
---

```{r knitr_init, echo=FALSE, cache=FALSE, message = FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(MASS)
library(dplyr)

## Global options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, prompt = FALSE,
                      tidy = TRUE, comment = NA, warning = FALSE, cache = TRUE,
                      fig.height = 4, fig.width = 7, fig.retina = 2,
                      fig.align = "center")
custom_theme <- theme_bw(base_family = "Open Sans") +
        theme(legend.position = "right",
              axis.title.x = element_text(size = 11,
                                          margin = margin(10, 0, 0, 0),
                                          face = "bold"),
              axis.title.y = element_text(size = 11,
                                          margin = margin(0, 10, 0, 0),
                                          face = "bold"),
              plot.title = element_text(family = "Open Sans"),
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank())
theme_set(custom_theme)
```

# Loading Data

밑의 코드는 고정입니다. 수정하지 말아주세요. :)

```{r}
library(caret)
library(ISLR)
library(e1071)
library(dplyr)
data(Auto)
head(Auto)
dim(Auto)
Auto <- Auto %>%
        mutate(mileage = factor(ifelse(Auto$mpg > median(Auto$mpg), 1, 0)))
set.seed(123)
split <- createDataPartition(y = Auto$mileage, p = 0.7, list = FALSE)
train <- Auto[split, ]
test <- Auto[-split, ]
train <- train[-c(1, 9)]
test <- test[-c(1, 9)]
```

# Data Information

### Data Description

Gas mileage, horsepower, and other information for 392 vehicles.

### Attributes Description

A data frame with 392 observations on the following  variables.

`mileage`
mileage, Good = 1, Bad = 0

`cylinders`
Number of cylinders between 4 and 8

`displacement`
Engine displacement (cu. inches)

`horsepower`
Engine horsepower

`weight`
Vehicle weight (lbs.)

`acceleration`
Time to accelerate from 0 to 60 mph (sec.)

`year`
Model year (modulo 100)

`origin`
Origin of car (1. American, 2. European, 3. Japanese)

The orginal data contained 408 observations but 16 observations with missing values were removed.

# Do SVM