---
title: "Diabetes Diagnosis"
author: "Jaeyoon Han"
output:
  html_document:
    highlight: pygments
---

```{r knitr_init, echo=FALSE, cache=FALSE, message = FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(MASS)
library(dplyr)

## Global options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, prompt = FALSE,
                      tidy = TRUE, comment = NA, warning = FALSE, cache = TRUE,
                      fig.height = 4, fig.width = 7, fig.retina = 2,
                      fig.align = "center")
custom_theme <- theme_bw(base_family = "Open Sans") +
        theme(legend.position = "right",
              axis.title.x = element_text(size = 11,
                                          margin = margin(10, 0, 0, 0),
                                          face = "bold"),
              axis.title.y = element_text(size = 11,
                                          margin = margin(0, 10, 0, 0),
                                          face = "bold"),
              plot.title = element_text(family = "Open Sans"),
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank())
theme_set(custom_theme)
```

# Loading Data

밑의 코드는 고정입니다. 수정하지 말아주세요. :)

```{r}
library(MASS)
library(dplyr)
data(Pima.tr)       # Training Data
data(Pima.te)       # Test Data

train_labels <- Pima.tr$type
test_labels <- Pima.te$type
Pima.tr$type <- NULL
Pima.te$type <- NULL

accuracy <- function(actual, predict){
        return(sum(actual == predict) / length(actual))
}


```

# Data Information

### Data Description

A population of women who were at least 21 years old, of Pima Indian heritage and living near Phoenix, Arizona, was tested for diabetes according to World Health Organization criteria. The data were collected by the US National Institute of Diabetes and Digestive and Kidney Diseases. We used the 532 complete records after dropping the (mainly missing) data on serum insulin.

### Attributes Description

These data frames contains the following columns:

`npreg` : 
number of pregnancies.

`glu` : 
plasma glucose concentration in an oral glucose tolerance test.

`bp` : 
diastolic blood pressure (mm Hg).

`skin` : 
triceps skin fold thickness (mm).

`bmi` : 
body mass index (weight in kg/(height in m)\^2).

`ped` : 
diabetes pedigree function.

`age` : 
age in years.

`type` : 
Yes or No, for diabetic according to WHO criteria.

# Do k-Nearest Neighbor

```{r}
library(MASS)
library(dplyr)
data(Pima.tr)
data(Pima.te)
str(Pima.tr)
str(Pima.te)
summary(Pima.tr)
summary(Pima.te)
```

```{r}
library(caret)
library(class)
library(reshape2)

train_labels <- Pima.tr$type
test_labels <- Pima.te$type
Pima.tr$type <- NULL
Pima.te$type <- NULL
diabetes <- knn(train = Pima.tr, test = Pima.te, cl = train_labels, k = 15)
confusionMatrix(diabetes, test_labels, positive = "No")

odds <- seq(1, 25, by = 2)
Result3 <- data.frame(k = NULL, Accuracy = NULL, Sensitivity = NULL,
                      Specificity = NULL, PosPredValue = NULL, NegPredValue = NULL)
for(i in odds){
        pred <- knn(train = Pima.tr, test = Pima.te, cl = train_labels, k = i)
        confMat <- confusionMatrix(pred, test_labels, positive = "No")
        currentResult <- data.frame(k = i, Accuracy = confMat$overall[1],
                                    Sensitivity = confMat$byClass[1],
                                    Specificity = confMat$byClass[2],
                                    PosPredValue = confMat$byClass[3],
                                    NegPredValue = confMat$byClass[4])
        Result3 <- bind_rows(Result3, currentResult)
}
Result3
# k = 21

moltenResult <- melt(Result3, id.vars = "k")
ggplot(data = moltenResult, aes(x = k, y = value, color = variable)) +
        geom_line()
```


```{r}
normalize <- function(x){
        return ((x - min(x)) / (max(x) - min(x)))
}

Pima <- dplyr::bind_rows(Pima.tr, Pima.te)
Pima_n <- as.data.frame(lapply(Pima, normalize))
Pima_n_tr <- Pima_n[1:200, ]
Pima_n_te <- Pima_n[201:nrow(Pima_n), ]

odds <- seq(1, 25, by = 2)
Result4 <- data.frame(k = NULL, Accuracy = NULL, Sensitivity = NULL, Specificity = NULL, PosPredValue = NULL, NegPredValue = NULL)
for(i in odds){
        pred <- knn(train = Pima_n_tr, test = Pima_n_te, cl = train_labels, k = i)
        confMat <- confusionMatrix(pred, test_labels, positive = "No")
        currentResult <- data.frame(k = i, Accuracy = confMat$overall[1], Sensitivity = confMat$byClass[1],
                Specificity = confMat$byClass[2], PosPredValue = confMat$byClass[3], NegPredValue = confMat$byClass[4])
        Result4 <- dplyr::bind_rows(Result4, currentResult)
}
Result4

moltenResult <- melt(Result4, id.vars = "k")
ggplot(data = moltenResult, aes(x = k, y = value, color = variable)) +
        geom_line()
```

```{r}
Pima <- dplyr::bind_rows(Pima.tr, Pima.te)
Pima_z <- as.data.frame(lapply(Pima, scale))
Pima_z_tr <- Pima_z[1:200, ]
Pima_z_te <- Pima_z[201:nrow(Pima_z), ]

Result5 <- data.frame(k = NULL, Accuracy = NULL, Sensitivity = NULL, Specificity = NULL, PosPredValue = NULL, NegPredValue = NULL)
for(i in odds){
        pred <- knn(train = Pima_z_tr, test = Pima_z_te, cl = train_labels, k = i)
        confMat <- confusionMatrix(pred, test_labels, positive = "No")
        currentResult <- data.frame(k = i, Accuracy = confMat$overall[1], Sensitivity = confMat$byClass[1],
                Specificity = confMat$byClass[2], PosPredValue = confMat$byClass[3], NegPredValue = confMat$byClass[4])
        Result5 <- dplyr::bind_rows(Result5, currentResult)
}
Result5

moltenResult <- melt(Result5, id.vars = "k")

ggplot(data = moltenResult, aes(x = k, y = value, color = variable)) +
        geom_line()
```

## ROC Curve

```{r}
library(ROCR)
library(plotROC)
pred <- knn(train = Pima_z_tr, test = Pima_z_te, cl = train_labels, k = 21, prob = TRUE)
pred_prob <- attributes(pred)$prob
fpr <- 1 - pred_prob
roc_df <- data.frame(fpr = fpr, class = as.numeric(test_labels)-1)

knn_roc <- ggplot(roc_df, aes(m = fpr, d = class)) + geom_roc()
knn_roc
calc_auc(knn_roc)
```

```{r}
pred_knn <- prediction(1 - attributes(pred)$prob, test_labels)
pred_knn <- performance(pred_knn, "tpr", "fpr")
plot(pred_knn, avg= "threshold", colorize=T, lwd=3, main="Voilà, a ROC curve!")
```
